The Hyperedge Event Model

### 2019-01-19 paper/revision1/HEM-reply.tex
revised memo

\begin{center}
\textbf{Authors' Responses to Associate Editor}
\end{center}
\begin{center}
\textsl{The Hyperedge Event Model}
\end{center}

Thank you for acknowledging our efforts and contributions, and also for your constructive suggestions, which are very helpful to improve the quality of our paper.

@@

First, we thank the editor...

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor.. \\

@@

@@

@@

\noindent  {\bf E5} \grey{\emph{ Some sentences are di¢ cult to understand:
Page 3: ``we define a probability measure ``MBG'' motivated by the Gibbs measure'' }}\\

>>>>

\begin{center}
\textsl{The Hyperedge Event Model}
\end{center}
\iffalse
Thank you for acknowledging our efforts and contributions, and also for your constructive suggestions, which are very helpful to improve the quality of our paper.

@@

First, we thank the editor for acknowledging our efforts and contributions, and also for your constructive suggestions, which are very helpful to improve the quality of our paper.

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor pointed out the lack of detailed and coherent explanation on the model in Section 2, suggesting better definition of variables and improvement on writing. We have significantly revised Section 2 by changing the order of subsections along with general rewriting---see E2 to E5 for details. \\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified some unusual notations which are not consistent with the literature. Instead of $A$ for nodes (which we got idea from SAOM as the Editor assumed) we now use $V$ for nodes (referring to vertex in network literature), and we also replaced $y$ by $z$ for time-related covariates---which are clearly stated in Section 2. We also added detailed definition on the variables and notations, such as the usage of subscripts $i$, $e$, $j$ right before Section 2.1. \\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} Following the Editor's suggestion, we changed the order of Equation (2.2) and (2.1) as well as their following texts to help readers' understandability. Moreover, we agree that the term ``intensity'' could be a confusing term so we revised the sentence withut using the term.\\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor expressed difficulty in understanding Section 2.2 and 2.3, and suggested further clarification on the variables $\tau$ and $\mu$. We moved Fig. 1 to earlier parts of Section 2 and briefly summarized the entire Section 2, such that the readers can understand Section 2.2 without reading Section 2.3. We also further explained the concepts and notations related to timestamp variables, $\tau$ and $\mu$, to avoid any confusion.\\

\noindent  {\bf E5} \grey{\emph{ Some sentences are difficult to understand:
Page 3: ``we define a probability measure ``MBG'' motivated by the Gibbs measure'' }}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} According to the Editor's comment, we revised the sentence mentioned above and also went through entire draft to revise sentences that were not clearly written before. \\
